Multi-Core Model Checking and Maximum Satisfiability Applied to Hardware-Software Partitioning

### 2015-09-28 Docs/TODAES/paper.tex
changes in benchmarks table
add Renato as co-author
review introduction

% Title portion
\author{
Alessandro Trindade
\affil{Federal University of Amazonas}
Hussama Ismail
\affil{Federal University of Amazonas}
Edilson Galv\~ao\
\affil{Federal University of Amazonas}
Helder Silva
\affil{Federal University of Amazonas}
Lucas Cordeiro\affil{Federal University of Amazonas}
}

@@

Nowadays, with the strong development of embedded systems, the design phase plays an important role. At early stages, the design is split into separated flows: hardware and software. The partitioning decision process, which deals with decisions upon which parts of the application have to be designed in hardware (HW) and which in software (SW), must be supported by any well-structured methodology. If not, this leads to a number of issues (design flow interruptions, redesigns, and undesired iterations) which affect the overall development process, the quality, and the lifecycle of the final system.

@@

Here, we exploit the availability of multi-core processors; in particular, SMT-based verification methods are applied to the HW-SW partition problem in three different ways using a multi-core ESBMC approach with OpenMP~\cite{Tang2009}: ESBMC-SS using a sequential-search (SS), ESBMC-PS using a parallel-search (PS), and ESBMC-PB using a binary-search (BS). Experimental results are compared to ILP (integral linear programming), GA (generic algorithms) in a multi-core version, and also to $\nu$Z, which supports only a single-core approach~\cite{Bjorner2015}. The ILP and GA algorithms are implemented with the optimization toolbox of Matlab~\cite{OpenMP1998}, while $\nu$Z is a built-in tool to the SMT solver Z3. All multi-core ESBMC approaches, together with $\nu$Z, are implemented with the Efficient SMT-based Context-Bounded Model Checker (ESBMC) tool~\cite{Cordeiro2012}.

@@

\begin{table}[h]
\centering
\caption {Description of Benchmarks.}
\small
\sffamily\footnotesize
\tabulinesep=6pt
\begin{tabular}[c]{m{1.5cm}m{0.8cm}m{0.8cm}m{3.8cm}}
  \toprule[1.5pt]
%  \head{Name} & \head{Nodes} & \head{Edges} & \head{Description}\\
  \midrule

\verb|CRC32| & \verb|25| & \verb|32| & \rmfamily 32-bit cyclic redundancy check ~\cite{Guthaus2001}\\
\hline
\verb|Patricia| & \verb|21| & \verb|48| & \rmfamily Routine to insert values in Patricia Tree ~\cite{Guthaus2001}\\
\hline

\verb|Dijkstra| & \verb|26| & \verb|69| & \rmfamily Computer shortest paths in a graph ~\cite{Guthaus2001}\\
\hline
\verb|Clustering| & \verb|150| & \verb|331| & \rmfamily Image segmentation algorithm in a medical application\\
\hline
\verb|RC6| & \verb|329| & \verb|448| & \rmfamily RC6 cryptography graph algorithm\\
\hline
\verb|Fuzzy| & \verb|261| & \verb|422| & \rmfamily Clustering algorithm based on fuzzy logic\\
\hline
\verb|Mars| & \verb|417| & \verb|600| & \rmfamily MARS cipher from IBM algorithm\\

  \bottomrule[1.5pt]
\end{tabular}
\label{Description-of-Benchmarks}
\end{table}

>>>>

% Title portion
\author{
Alessandro Trindade
\affil{Federal University of Amazonas}
Hussama Ismail
\affil{Federal University of Amazonas}
Edilson Galv\~ao\
\affil{Federal University of Amazonas}
Renato Degelo\
\affil{Federal University of Amazonas}
Helder Silva
\affil{Federal University of Amazonas}
Lucas Cordeiro\affil{Federal University of Amazonas}
}

@@

Nowadays, with the strong development of embedded systems, the design phase plays an important role. At early stages, the design is split into separated flows: hardware and software. The partitioning decision process, which deals with decisions upon which parts of the application have to be designed in hardware (HW) and which one in software (SW), must be supported by any well-structured methodology. If there is no methodology support, a number of issues, {\it e.g.}, design flow interruptions, redesigns, and undesired iterations may affect the overall development process, the quality, and the life-cycle of the final system.

@@

Here, we exploit the availability of multi-core processors; in particular, SMT-based verification methods are applied to the HW-SW partition problem in three different ways using a multi-core ESBMC approach with OpenMP~\cite{Tang2009}: ESBMC-SS using a sequential-search (SS), ESBMC-PS using a parallel-search (PS), and ESBMC-PB using a binary-search (BS). Experimental results are compared to ILP (integral linear programming), GA (generic algorithms) in a multi-core version, and also to $\nu$Z, which supports only a single-core approach~\cite{Bjorner2015}. The ILP and GA algorithms are implemented with the optimization toolbox of Matlab~\cite{OpenMP1998}, while $\nu$Z is a built-in tool to the SMT solver Z3. All multi-core ESBMC approaches, together with $\nu$Z, are implemented with the ESBMC tool~\cite{Cordeiro2012}.

@@

\begin{table}[h]
\centering
\caption {Description of Benchmarks.}
\small
\sffamily\small
\tabulinesep=6pt
\begin{tabular}[c]{m{1.9cm}m{0.9cm}m{0.9cm}m{9.0cm}}
\\
\toprule[1.5pt]
\textbf{Name} & \textbf{Nodes} & \textbf{Edges} & \textbf{Description}\\
\midrule
\\
\verb|CRC32| & \verb|25| & \verb|32| & \normalsize 32-bit cyclic redundancy check ~\cite{Guthaus2001}\\
\\
\hline
\\
\verb|Patricia| & \verb|21| & \verb|48| & \rmfamily Routine to insert values in Patricia Tree ~\cite{Guthaus2001}\\
\\
\hline
\\
\verb|Dijkstra| & \verb|26| & \verb|69| & \rmfamily Computer shortest paths in a graph ~\cite{Guthaus2001}\\
\\
\hline
\\
\verb|Clustering| & \verb|150| & \verb|331| & \rmfamily Image segmentation algorithm in a medical application\\
\\
\hline
\\
\verb|RC6| & \verb|329| & \verb|448| & \rmfamily RC6 cryptography graph algorithm\\
\\
\hline
\\
\verb|Fuzzy| & \verb|261| & \verb|422| & \rmfamily Clustering algorithm based on fuzzy logic\\
\\
\hline
\\
\verb|Mars| & \verb|417| & \verb|600| & \rmfamily MARS cipher from IBM algorithm\\
\\
\bottomrule[1.5pt]
\end{tabular}
\label{Description-of-Benchmarks}
\end{table}
